---
title: "analysis_markdown.Rd"
output: html_document
---
# A minimal R Markdown example
 
A quote:
 
> Markdown is not LaTeX.
 
To compile me, run this in R:
 
    library(knitr)
    knit('analysis.Rmd')


# Introduction
The RMarkdown file executes the same code as in analysis... with slightly more explanation. We include this file to show how to use RMarkdown for creating reports.

## Install and load the packages first. 
```{r install_packages, echo=TRUE}
install.packages(c("ggmap"))
library(dplyr)
library(ggplot2)

```

## Load the data:
```{r load_data}
crimedata <- read.csv("SFPD_Incidents_-_Current_Year__2015_.csv")
```

## We will look at ASSAULT that happen on a Monday. We define the variables and the function that filtered out data here.
```{r define_functions}
crime <- 'ASSAULT'
day <- 'Monday'
SF_COORDINATES <- c(37.76, -122.45)

# Define function to filter the data
get_filtered <- function(crime, day){
  filter(crimedata,crimedata$DayOfWeek == day & crimedata$Category == crime)
}
```

##Explore the data
We start by filtering the data, seeing all the different types of crimes that are tracked, and inspecting the form of the data.
```{r explore_data}
filtered_crimedata<- get_filtered(crime, day)
print(unique(filtered_crimedata$Category), max.levels = 40, quote=TRUE)
head(filtered_crimedata)
```

### Mapping the crimes
```{r map_crimes}
library(ggmap)
sf <- get_map(location = rev(SF_COORDINATES), zoom = 12, color='bw')
map_points <- ggmap(sf) + geom_point(data=filtered_crimedata, 
                       aes(x=X, y=Y),size=1, color='red') +
  labs(x="Longitude", y="Latitude")

map_points
dev.copy(png,'simple_map.png')
dev.off()
```

## K-means to find the clusters
```{r kmeans}
X <- data.frame(filtered_crimedata$X, filtered_crimedata$Y)
Y<-kmeans(X,4)
X_with_clusters <- cbind(X, Y$cluster)
names(X_with_clusters)[3] <- ".cluster"
kmeans_plot <- ggmap(sf) + geom_point(data=X_with_clusters, 
                                     aes(x=filtered_crimedata.X, y=filtered_crimedata.Y),
                                     size=1, color=X_with_clusters$.cluster) +
  labs(x="Longitude", y="Latitude")
kmeans_plot
dev.copy(png,'kmeans.png')
dev.off()
```

## Linear regression
Let's look at all crimes and see what times they occur. We'll try to interpolate with linear regression.
```{r lin_reg}
time_data <- as.POSIXct(crimedata$Time,format="%H:%M")
df <- data.frame(time =  time_data)
df$time = strptime(df$time, "%Y-%m-%d %H:%M") 
df$x2 = paste0(substr(df$time, 1, 14), "00:00")
df2 = data.frame(table(df$x2))
names(df2) = c("Hour","Freq")
df2$Freq<-as.numeric(df2$Freq)
df2$Hour<-as.numeric(df2$Hour)

fit <- lm(formula = Freq ~ Hour, data=df2)
summary(fit)
p <-qplot(df2$Hour, df2$Freq)
p+ geom_abline(aes(intercept=fit$coefficients[1], 
                   slope=fit$coefficients[2]), col="red")
dev.copy(png,'linear_regression.png')
dev.off()
```

## Random Forest regression
```{r random_forest}
library(randomForest)
rf <- randomForest(Freq ~ Hour, data = df2, ntree=24)
pred <- data.frame(predict(rf, df2))
names(pred)[1] <- "Pred"
pred$Hour <- df2$Hour
p <-ggplot(df2, aes(Hour, Freq, color = "Actual") ) + geom_point(alpha=1)
p<- p + geom_point(aes(x = Hour, y = Pred, color="Predicted"), data=pred, alpha =1)
p
dev.copy(png,'rf.png')
dev.off()
```